%-------------------------
% Resume in LaTeX
% Author: Ritabrata Chakraborty
% Based on: https://github.com/Ritabrata-Chakraborty/Research-Resume
% License: MIT
%-------------------------

\documentclass[letterpaper,10pt]{article}

%----------PACKAGES----------
\usepackage{latexsym}
\usepackage[margin=0.5in]{geometry}   % 0.5-inch margins
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

%----------PAGE SETUP----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}  % spacing in tabular

%----------SECTION FORMATTING----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-10pt}]

%----------PDF SETUP----------
\pdfgentounicode=1

%------------------------------------------
%           CUSTOM COMMANDS
%------------------------------------------

% Resume item (bullet point)
\newcommand{\resumeItem}[1]{
  \item \small{#1\vspace{-2pt}}
}

% Resume subheading (e.g., job, degree)
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{#2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}

% Resume sub-subheading (e.g., role or subsection under job)
\newcommand{\resumeSubSubheading}[2]{
  \vspace{0pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textit{\small #1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-6pt}
}

% Resume project heading
\newcommand{\resumeProjectHeading}[2]{
  \vspace{0pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \small #1 & #2 \\
  \end{tabular*}\vspace{-6pt}
}

% Resume subitem (optional nested bullet)
% \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% Bullet symbol style
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%------------------------------------------
%         LIST ENVIRONMENTS
%------------------------------------------

% Subheading list (e.g., Education, Experience)
\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0.10in, label={}]\vspace{6pt}
}
\newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}
}

% Item list (bullet points under subheadings)
\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=0.18in]
}
\newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{-6pt}
}

%------------------------------------------
%           SKILL LIST (no bullets)
%------------------------------------------

% Start of skill list (clean, no bullet points)
\newcommand{\nbresumeItemListStart}{
  \begin{itemize}[leftmargin=0.10in, label={}, itemsep=2pt, parsep=2pt]\vspace{6pt}
}

% Individual skill line
\newcommand{\nbresumeItem}[1]{
  \item \small{#1}
}

% End of skill list
\newcommand{\nbresumeItemListEnd}{
  \end{itemize}\vspace{-6pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\huge Ritabrata Chakraborty} \\ [6pt]
  \small
  {\color{blue}\href{https://github.com/Ritabrata-Chakraborty}{GitHub} $|$
  \href{https://scholar.google.com/citations?user=JikCewwAAAAJ&hl=en}{Google Scholar} $|$
  \href{https://www.researchgate.net/profile/Ritabrata-Chakraborty-3/research}{ResearchGate} $|$
  \href{https://www.scopus.com/authid/detail.uri?authorId=60101248100}{Scopus} $|$
  \href{https://ritabrata-chakraborty.github.io/Portfolio/}{Portfolio} $|$
  \href{https://www.linkedin.com/in/ritabrata-chakraborty-a63268251/}{LinkedIn} $|$
  \href{mailto:resume@gmail.com}{resume@gmail.com} $|$ \href{tel:+999999999999}{+99 99999 99999}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Birla Institute of Technology and Science, Pilani (BITS Pilani)}{Rajasthan, India}
    {B.E. in Mechanical Engineering | Minor in Data Science, \textbf{CGPA: X.XX/10 (Final: X.XX/10)}}{Oct '22 – May '26}
    \resumeItemListStart
      \resumeItem{\textbf{Institute Merit-cum-Need Scholarship} — Consecutive Recipient (Top X\% of Students)}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------PUBLICATIONS----------
\section{Publications \& Presentations}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Journal Publications}}{}
  \resumeItemListStart
    \resumeItem{
        K. Kishore, \textbf{R. Chakraborty}, and S. Singh,
        \textbf{\textit{``Exploring Unknown Indoor Environments with Drones Using a Multi-Critic DDPG Architecture.''}}
        Under review at \textbf{IEEE Transactions on Artificial Intelligence (TAI)}, 2026.
        \color{blue}\href{https://drive.google.com/file/d/1Uimegpx43p9dfY7lvgPU_LR3ERb3-YJP/view}{\textbf{\faExternalLink*}}
        }
        \vspace{4pt}

        \resumeItem{
        \textbf{R. Chakraborty} and P. Kundu,
        \textbf{\textit{``Beyond ImageNet: VQGAN-Based Augmentation and Optimized Perceptual Metrics for Bearing Fault Diagnosis.''}}
        Manuscript in preparation for \textbf{IEEE Transactions on Industrial Informatics, (TII)}, 2026.
        \color{blue}\href{https://drive.google.com/file/d/1o26-f-Rp7bS6296O3eEEwFyPNoUBL_Gq/view?usp=drive_link}{\textbf{\faExternalLink*}}
        }

    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Conference Publications}}{}
  \resumeItemListStart
    \resumeItem{
        Y. Wang, H. He, Y. Cao, J. Liang, \textbf{R. Chakraborty}, and G. A. Sartoretti,
        \textbf{\textit{``CogniPlan: Uncertainty-Guided Path Planning with Conditional Generative Layout Prediction.''}}
        Accepted at the \textbf{Conference on Robot Learning (CoRL)}, 2025.
        \color{blue}\href{https://arxiv.org/pdf/2508.03027}{\textbf{\faExternalLink*}}
        }
        \vspace{4pt}

        \resumeItem{
        \textbf{R. Chakraborty}, T. Mian, and P. Kundu,
        \textbf{\textit{``An Efficient Approach for Synthetic Data Generation and Fault Diagnosis for Rotating Machinery.''}}
        Published in \textbf{IET Conference Proceedings},
        \textbf{Prognostics and System Health Management Conference (PHM)}, 2025.
        \color{blue}\href{https://ieeexplore.ieee.org/document/11090096}{\textbf{\faExternalLink*}}
        }
        \vspace{4pt}

        \resumeItem{
        K. Kishore and \textbf{R. Chakraborty},
        \textbf{\textit{``Path Planning of Low-Altitude UAV for Tree Canopy Tracking and Orchard Monitoring.''}}
        Filed as \textbf{Intellectual Property}, 2025.
        \color{blue}\href{https://drive.google.com/file/d/1TZ-1WKuYXeAOZaP7R5TnSufCdyz3sn4a/view}{\textbf{\faExternalLink*}}
        }
        \vspace{4pt}

        \resumeItem{
        \textbf{R. Chakraborty} and M. S. Dasgupta,
        \textbf{\textit{``Hockey3D: A Public Field Hockey Shot Trajectory Dataset with 3D Reconstruction and Shot Type Classification.''}}
        Manuscript in preparation for the \textbf{Conference on Computer Vision and Image Processing (CVIP)}, 2026.
        \color{blue}\href{https://drive.google.com/file/d/1XSeU50fM_yJUn0u2wcNOM2itZovqAA2V/view}{\textbf{\faExternalLink*}}
        }

    % \vspace{4pt}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience -- Robotics \& Computer Vision}
\resumeSubHeadingListStart
  \resumeSubheading
    {Multi-Critic Off-Policy RL for Autonomous Indoor Drone Navigation \color{blue}\href{https://github.com/Ritabrata-Chakraborty/Quadcopter-RL-Off-Policy-Velocity-Control/tree/main}{\faExternalLink*}}{}
    {Supervisor: {\color{blue}\href{https://ieeexplore.ieee.org/author/37085653936}{Dr. Kaushal Kishore,}} Principal Scientist, CSIR-CEERI}{Jan '26 -- Present}
  \resumeItemListStart
      \resumeItem{Orchestrated a multi-critic RL framework for continuous control of quadrotor exploration in unknown indoor environments.}
      \resumeItem{Implemented a hybrid reward formulation integrating artificial potential fields and prioritized experience replay to improve exploration efficiency and sample utilization.}
  \resumeItemListEnd

 \resumeSubheading
    {Vision-Attention-Driven Autonomous Navigation with Semantic Understanding}{}
    {Supervisor: {\color{blue}\href{https://cde.nus.edu.sg/me/staff/sartoretti-guillaume-a/}{Dr. Guillaume Sartoretti,}} Assistant Professor, MARMoT Lab, NUS}{Aug '25 -- Present}
  \resumeItemListStart
    \resumeItem{Enhanced \textit{\color{blue}\href{https://yizhuo-wang.com/cogniplan/}{CogniPlan}} with cross-attention between frontier and node embeddings to enrich node representations.}
    \resumeItem{Incorporated {\color{blue}\href{https://general-navigation-models.github.io/vint/}{Visual Navigation Transformer (ViNT)}} to capture semantic context for adaptive exploration strategies.}
  \resumeItemListEnd

  \resumeSubheading
    {ML Intern $|$ Uber (AI Solutions)}{}
    {Supervisor: {\color{blue}\href{https://in.linkedin.com/in/malreddysid}{Mr. Siddarth Malreddy,}} Tech Lead Manager \& {\color{blue}\href{https://www.linkedin.com/in/ishannigam/}{Mr. Ishan Nigam,}} Senior ML Engineer, Uber}{July '25 -- Dec '25}
  \resumeItemListStart
    \resumeItem{Augmented {\color{blue}\href{https://www.uber.com/us/en/ai-solutions/annotation/}{uLabel}} with object tracking for automated RGB/IR video annotation, reducing manual effort.}
    \resumeItem{Deployed XGBoost anomaly detection (mAP50: 75\%) to flag perturbed bboxes in human-in-the-loop tracking validation.}
  \resumeItemListEnd

  \resumeSubheading
    {Design and Development of Smart Automated Field Hockey Ball Launcher \color{blue}\href{https://drive.google.com/file/d/1h7X9fIiih37ivgERVR-wbWsDEil0qvpI/view?usp=drive_link}{\faExternalLink*}}{}
    {Supervisor: {\color{blue}\href{https://www.bits-pilani.ac.in/pilani/m-s-dasgupta/}{Dr. Mani Shankar Dasgupta,}} Associate Professor, BITS Pilani}
    {Apr '24 -- Oct '25}

    \resumeSubSubheading
      {\textbf{\hspace{4pt}Physics-Based Launcher Mechanical Design and FEM Analysis}}{}
    \resumeItemListStart
      \resumeItem{Fabricated programmable launcher achieving 150 km/h using CFRP composite and stainless steel components.}
      \resumeItem{Performed FEM analysis and CAD using Fusion 360, achieving safety factor 2.07 at 496 RPM.}
    \resumeItemListEnd

    \resumeSubSubheading
      {\textbf{\hspace{4pt}Computer Vision Pipeline for 3D Trajectory Reconstruction and Shot Classification}}{}
    \resumeItemListStart
      \resumeItem{Devised 3D ball localization from monocular videos using diameter-based depth and {\color{blue}\href{https://github.com/mguti97/PnLCalib}{PnLCalib}}  (0.76m RMSE).}
      \resumeItem{Developed TCN-attention classifier fusing trajectory and statistical features, achieving 96.4\% classification accuracy.}
    \resumeItemListEnd

  \resumeSubheading
    {Uncertainty-Guided Path Planning via Conditional Layout Prediction \color{blue}\href{https://yizhuo-wang.com/cogniplan/}{\faExternalLink*}}{}
    {Supervisor: {\color{blue}\href{https://cde.nus.edu.sg/me/staff/sartoretti-guillaume-a/}{Dr. Guillaume Sartoretti,}} Assistant Professor, MARMoT Lab, NUS}{Mar '25 -- Aug '25}
  \resumeItemListStart
    \resumeItem{Adapted multiple image-based exploration planners into ROS pipelines for evaluation in the \color{blue}\href{https://www.cmu-exploration.com/}{CMU Exploration Environment}.}
    \resumeItem{Supported the development and benchmarking of \textit{\color{blue}\href{https://yizhuo-wang.com/cogniplan/}{CogniPlan}}, achieving up to 17.7\% shorter exploration paths and 3.9\% improved navigation efficiency over state-of-the-art baselines across 100+ unseen maps.}
  \resumeItemListEnd

  \resumeSubheading
    {Monocular Vision-Based UAV Navigation for Orchard Monitoring \color{blue}\href{https://github.com/Ritabrata-Chakraborty/Monocular-Vision-Based-UAV-Navigation-for-Orchard-Monitoring.git}{\faExternalLink*}}{}
    {Supervisor: {\color{blue}\href{https://ieeexplore.ieee.org/author/37085653936}{Dr. Kaushal Kishore,}} Principal Scientist, CSIR-CEERI}{Jan '24 -- Feb '25}
  \resumeItemListStart
    \resumeItem{Engineered a UAV-based orchard monitoring system using YOLOv11 (Box mAP50: 95.5\%, Mask mAP50: 96.5\%).}
    \resumeItem{Programmed B-spline trajectory logic and implemented custom yaw-roll controller to minimize drift under wind.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXP _ PM-----------
\section{Experience -- Predictive Maintenance}
\resumeSubHeadingListStart
  \resumeSubheading
    {Synthetic Sensor Data Generation and Fault Classification for Bearing Systems}{}
    {Supervisor: {\color{blue}\href{https://www.kuleuven.be/wieiswie/en/person/00155770}{Dr. Pradeep Kundu,}} Assistant Professor, KU Leuven}{Sep '24 -- Present}

  \resumeSubSubheading
    {\textbf{\hspace{4pt}Auxiliary Classifier WGAN-GP for Time-Series Sensor Data Generation} {\color{blue}\href{https://github.com/Ritabrata-Chakraborty/An-Efficient-Approach-for-Synthetic-Data-Generation-and-Fault-Diagnosis-for-Rotating-Machinery}{\faExternalLink*}}}{}
  \resumeItemListStart
    \resumeItem{Built ACWGAN-GP with TCN discriminator to augment minority fault classes, reaching $\sim$100\% classification accuracy.}
    \resumeItem{Evaluated synthetic data by comparing real and generated FFT spectra using PCC, Cosine Similarity, MMD, and KL Divergence.}
  \resumeItemListEnd

\resumeSubSubheading
    {\textbf{\hspace{4pt}VQGAN-Based Augmentation and Optimized Perceptual Metrics for Bearing Fault Diagnosis}}{}
  \resumeItemListStart
    \resumeItem{Developed Conditional {\color{blue}\href{https://arxiv.org/pdf/2012.09841}{VQGAN}} framework with EMA-updated codebook and Transformer-based autoregressive prior for faulty scalogram synthesis, mitigating class imbalance and enhancing structural realism.}
    \resumeItem{Designed optimized {\color{blue}\href{https://arxiv.org/abs/1801.03924}{LPIPS}}-based perceptual training and refined {\color{blue}\href{https://arxiv.org/pdf/1706.08500}{FID}} evaluation via domain-adapted layer selection, and developed {\color{blue}\href{https://ieeexplore.ieee.org/document/10294257}{LiteFormer}} variants to validate augmentation gains in bearing fault classification.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Autonomous Drone Navigation $|$ MathWorks Global Student Drone Challenge 2025}}
    {\textit{Mar '25 -- Apr '25}}
  \resumeItemListStart
    \resumeItem{Programmed vision-based control for Parrot Mambo drone using masking, ray-tracing, and closed-loop yaw control.}
    \resumeItem{Optimized speed control and zone-based auto-landing to reduce track completion time.}
  \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{ExoMy Rover Navigation and UR3 Arm Motion Planning $|$ ERC 2023 Remote \color{blue}\href{https://drive.google.com/file/d/1qAeYAupdwq-eb-d-lgASr4xD_Kj0AXmk/view?usp=drive_link}{\faExternalLink*}}}
    {\textit{Apr '23 -- Sep '23}}
  \resumeItemListStart
    \resumeItem{Navigated ExoMy rover using ArUco detection, Ackermann steering, and spot turns for autonomous hazard avoidance.}
    \resumeItem{Calibrated UR3 arm with MoveIt and OMPL planner for collision-free manipulation (98\% success).}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%--------Leadership------
\section{Leadership \& Teaching}
\resumeSubHeadingListStart
  \resumeSubheading
    {President \& Secretary}{}
    {Mechanical Engineering Association (MEA), BITS Pilani}{Jun '24 – Present}
  \resumeItemListStart
    \resumeItem{Coordinated 10+ events and career sessions for 300+ students, facilitating technical exposure and alumni interaction.}
    \resumeItem{Managed production of 500+ merchandise items and led outreach, boosting student participation by 20\%.}
  \resumeItemListEnd

  \resumeSubheading
    {President \& Tech Fest Coordinator}{}
    {Indian Society of Heating, Refrigerating, and Air Conditioning Engineers (ISHRAE), BITS Pilani}{Oct '24 – Jul '25}
  \resumeItemListStart
    \resumeItem{Led a team of 25+ members to organize 4+ technical workshops with HVAC industry experts.}
    \resumeItem{Hosted 3 competitions and networking events, engaging 200+ students in HVAC innovation and awareness.}
  \resumeItemListEnd

  \resumeSubheading
    {Project Manager}{}
    {Tinkerer's Lab (TL), BITS Pilani}{May '24 – Jul '25}
  \resumeItemListStart
    \resumeItem{Supervised 5 interdisciplinary robotics teams (30+ members) on Micromouse and Hexapod projects.}
    \resumeItem{Oversaw lab resources, conducted weekly reviews, and mentored 50+ students in hands-on technical skills.}
  \resumeItemListEnd

  \resumeSubheading
    {Teaching Assistant}{}
    {CS F320: Foundations of Data Science, BITS Pilani}{Jan '26 – Present}
  \resumeSubSubheading
    {ME F218: Advanced Mechanics of Solids, BITS Pilani}{Jan '25 – May '25}
  \resumeSubSubheading
    {ME F216: Materials Science and Engineering, BITS Pilani}{Sep '24 – Dec '24}

  \resumeItemListStart
    \resumeItem{Assisted 100+ students in labs and tutorials, clarifying concepts and linking theory to practical applications.}
    \resumeItem{Evaluated assignments and supported faculty in delivering high-impact teaching sessions.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Achievements}
\resumeSubHeadingListStart
  \resumeSubheading
    {\textbf{3\textsuperscript{rd} Place} — MathWorks Global Drone Student Challenge 2025}{\textit{Mar '25}}
    {}{}
    % {MathWorks}{}
  \vspace{-14pt}
  \resumeSubheading
    {\textbf{Finalist} — AI for Space and Geospatial Innovation (ISRO Immersion Challenge) \color{blue}\href{https://drive.google.com/file/d/16G0VYC5aEpGW_xqj6y0GRwX1Hb5cWeJk/view?usp=drive_link}{\faExternalLink*}}{\textit{Jul '24}}
    {}{}
    % {CIE–IIITH}{}
  \vspace{-14pt}
  \resumeSubheading
    {\textbf{Top 15 Overall, Top 5 in College} — American Express Campus Challenge 2024 \color{blue}\href{https://drive.google.com/file/d/1oC9seJ8GRzicnij6xViUjAum3Zq5Vjlr/view?usp=drive_link}{\faExternalLink*}}{\textit{Jul '24}}
    {}{}
    % {American Express}{}
  \vspace{-14pt}
  \resumeSubheading
    {\textbf{5\textsuperscript{th} Place} \& \textbf{Best Maintenance Award} — European Rover Challenge 2023 (Remote Finals)}{\textit{Sep '23}}
    {}{}
    % {European Space Foundation}{}
  \vspace{-14pt}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\nbresumeItemListStart
  \nbresumeItem{
  \textbf{Relevant Courses:} Machine Learning, Deep Learning, Foundations of Data Science, Applied Statistical Methods, Linear Algebra, Computer Programming, Engineering Optimization, Differential Equations, Design of Machine Elements, Digital Twins}
  \nbresumeItem{\textbf{Programming Languages:} Python, C++, C, Shell (Linux)}
  \nbresumeItem{\textbf{Robotics \& Simulation:} ROS (with Gazebo, Rviz), MAVROS, Navigation Stack, MoveIt, AirSim, Unity, Unreal Engine, MATLAB, Simulink, QGIS}
  \nbresumeItem{\textbf{Machine Learning:} PyTorch, TensorFlow, Scikit-Learn, OpenCV, Open3D, Matplotlib, Weights \& Biases (W\&B)}
  % \textbf{Cloud \& DevOps:} AWS (S3, EC2, Lambda), Google Cloud Platform (GCP), Docker, Git, GitHub Actions
  \nbresumeItem{\textbf{Hardware \& Embedded Systems:} NVIDIA Jetson (Nano, Orin), Raspberry Pi, Arduino, IMUs, Stereo Camera, 3D LiDAR}
  % \textbf{GPU Computing:} CUDA, cuDNN, TensorRT
  \nbresumeItem{\textbf{CAD \& Mechanical Simulation:} ANSYS Mechanical, SolidWorks, Fusion 360}
\nbresumeItemListEnd


% -------------------------------------------

\newpage

%-----------LINKS-----------
\section*{Reference Links}

\vspace{6pt}

\subsection*{Contact \& Professional Profiles}
\nbresumeItemListStart
  \nbresumeItem{Google Scholar: \color{blue}\url{https://scholar.google.com/citations?user=JikCewwAAAAJ&hl=en}}
  \nbresumeItem{Personal Homepage: \color{blue}\url{https://ritabrata-chakraborty.github.io/Portfolio/}}
  \nbresumeItem{LinkedIn: \color{blue}\url{https://www.linkedin.com/in/ritabrata-chakraborty-a63268251/}}
\nbresumeItemListEnd

\subsection*{Publications \& Presentations}
\nbresumeItemListStart
  \nbresumeItem{Exploring Unknown Indoor Environments with Drones Using a Multi-Critic DDPG Architecture (IEEE TAI 2026) \break
  {Draft: \color{blue}\url{https://drive.google.com/file/d/1Uimegpx43p9dfY7lvgPU_LR3ERb3-YJP/view}}}
  \nbresumeItem{Beyond ImageNet: VQGAN-Based Augmentation and Optimized Perceptual Metrics for Bearing Fault Diagnosis (IEEE TII 2026) \break
  {Draft: \color{blue}\url{https://drive.google.com/file/d/1o26-f-Rp7bS6296O3eEEwFyPNoUBL_Gq/view?usp=drive_link}}}
  \nbresumeItem{Hockey3D: A Public Field Hockey Shot Trajectory Dataset with 3D Reconstruction and Shot Type Classification (CVIP 2026) \break
  {Draft: \color{blue}\url{https://drive.google.com/file/d/1XSeU50fM_yJUn0u2wcNOM2itZovqAA2V/view?usp=drive_link}}}
  \nbresumeItem{CogniPlan: Uncertainty-Guided Path Planning with Conditional Generative Layout Prediction (CoRL 2025) \break
  {Paper: \color{blue}\url{https://arxiv.org/pdf/2508.03027}} \break
  {Project: \color{blue}\url{https://yizhuo-wang.com/cogniplan/}}}
  \nbresumeItem{An Efficient Approach for Synthetic Data Generation and Fault Diagnosis for Rotating Machinery (PHM 2025) \break
  {Paper: \color{blue}\url{https://digital-library.theiet.org/doi/abs/10.1049/icp.2025.2364}}}
  \nbresumeItem{Path Planning of Low-Altitude UAV for Tree Canopy Tracking and Orchard Monitoring (Intellectual Property 2025) \break
  {Draft: \color{blue}\url{https://drive.google.com/file/d/1TZ-1WKuYXeAOZaP7R5TnSufCdyz3sn4a/view?usp=sharing}}}
\nbresumeItemListEnd

\subsection*{Projects}
\nbresumeItemListStart
  \nbresumeItem{ExoMy Rover Navigation (ERC 2023 Remote) \break
  {Report: \color{blue}\url{https://drive.google.com/file/d/1qAeYAupdwq-eb-d-lgASr4xD_Kj0AXmk/view?usp=drive_link}}}
\nbresumeItemListEnd

\subsection*{Awards \& Achievements}
\nbresumeItemListStart
  \nbresumeItem{AI for Space and Geospatial Innovation (ISRO) \break
  {Presentation: \color{blue}\url{https://drive.google.com/file/d/16G0VYC5aEpGW_xqj6y0GRwX1Hb5cWeJk/view?usp=drive_link}}}
  \nbresumeItem{American Express Campus Challenge 2024 \break
  {Presentation: \color{blue}\url{https://drive.google.com/file/d/1oC9seJ8GRzicnij6xViUjAum3Zq5Vjlr/view?usp=drive_link}}}
\nbresumeItemListEnd


\end{document}
